Descriptive visualizations

### 2014-02-11 descriptive_analysis.Rmd
Changed the toc font size in css
First pages commit
Getting back to business. Nothing changed, but rerunning the script.
Pientä päivtystä. Huomenna iso remmi päälle

# Descriptive visualizations

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions")
library(knitr)
library(markdown)
knit2html('descriptive_analysis.Rmd', 
          stylesheet="~/workspace/web/css/rmarkdown.css",
          options = c('toc', markdown::markdownHTMLOptions(TRUE)))
```

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=TRUE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=10)
```

>>>>

---
title: Descriptive visualizations
output:
  html_document:
    toc: true
    theme: flatly
---

### 2014-02-11 loadClean.Rmd
Pientä päivtystä. Huomenna iso remmi päälle

@@

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=TRUE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=12)
```

@@

```{rLoadClean7, eval=TRUE}
#######
# Quality of governance

getQog <- function(data = "basic",
                   country = "all", 
                   indicator = "undp_hdi",
                   year = "all") {
# URL's for different data's
  basicURL <- "http://www.qogdata.pol.gu.se/data/qog_bas_ts_30aug13.csv"
  standardURL <- "http://www.qogdata.pol.gu.se/data/qog_std_ts_15may13.csv"
  socialPolicyURL <- "http://www.qogdata.pol.gu.se/data/qog_soc_tsl_4apr12.csv"

>>>>

---
title: Descriptive visualizations
output:
  html_document:
    toc: true
    theme: flatly
---

@@

@@

```{rLoadClean7, eval=TRUE}
#######
# Quality of governance
getQog <- function(data = "basic",
                   country = "all", 
                   indicator = "undp_hdi",
                   year = "all") {
# URL's for different data's
  basicURL <- "http://www.qogdata.pol.gu.se/data/qog_bas_ts_30aug13.csv"
  standardURL <- "http://www.qogdata.pol.gu.se/data/qog_std_ts_15may13.csv"
  socialPolicyURL <- "http://www.qogdata.pol.gu.se/data/qog_soc_tsl_4apr12.csv"
